---
title: "precision curve stat"
author: "Juechen Yang"
date: "7/16/2021"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Import all data from csv files
```{r}

library(tidyverse)
file_dir = "./Precision_20targets/"
out_dir = "./outputs/"
total_df = paste(file_dir, list.files(pattern = "*.csv", path = file_dir), sep = "/") %>% map_df(~read_csv(.))
#get the real probability of precision
total_df$precision = total_df$precision/100
#remove  RFs, NNs, and cML100
total_df = total_df[!grepl("RF|NN|cML100", total_df$group),]
total_df = data.frame(total_df)

#import median data
median_df = read.csv("median_prec.csv", header = T)
median_df = median_df[!grepl("RF|NN|cML100", median_df$group),]
median_df$median_prec = median_df$median_prec/100

median_df_0.1_5 = median_df[median_df$size<=5, ]
median_df_0.1_1 = median_df[median_df$size<=1, ]

#remove redundant column for both df
total_df = total_df[,-1]
median_df = median_df[,-1]

#replace precision 0 with 0.01
total_df_no_zero = total_df
total_df_no_zero["precision"] = ifelse(total_df_no_zero["precision"]==0, 0.01, total_df_no_zero[,"precision"])
```

# Perform ks test pairwisely
```{r}
bin_size = 0.025
ks_test_pairwise = function(v, df, precision_var, alternative){
  x = df[df$group==v[1],precision_var]
  y = df[df$group==v[2],precision_var]
  hx = hist(x, breaks = seq(0,1,bin_size), plot = F)
  hx$density = hx$counts/sum(hx$counts)
  hy = hist(y, breaks = seq(0,1,bin_size), plot = F)
  hy$density = hy$counts/sum(hy$counts)
  res.ks = ks.test(hx$density, hy$density, alternative = alternative)
  return(c("comparison"=paste0(v[1],"-", v[2]), res.ks$statistic, "p.value"=res.ks$p.value))
}
```

# Perform kl Divergence test pairwisely
```{r}
kld_test_pairwise = function(v, df, precision_var){
  x = df[df$group==v[1],precision_var]
  y = df[df$group==v[2],precision_var]
  hx = hist(x, breaks = seq(0,1,bin_size), plot = F)
  hx$density = hx$counts/sum(hx$counts)
  hy = hist(y, breaks = seq(0,1,bin_size), plot = F)
  hy$density = hy$counts/sum(hy$counts)
  if(df$size[1]==0.1){
    print(paste0(v[1],"-", v[2]))
    print(hx$counts)
    print(hy$counts)
    print(hx$density)
    print(hy$density)
  }
  res.KLD = LaplacesDemon::KLD(hx$density,hy$density)
  return(c("comparison"=paste0(v[1],"-", v[2]), "KLD" = res.KLD$intrinsic.discrepancy))
}
```

## Using all targets df to do ks test
```{r}
lib_size_repo = unique(total_df$size)
alt_methods = c("two.sided", "less", "greater")
for(i in seq(1, length(lib_size_repo))){
  sub_total_df = total_df[total_df$size==lib_size_repo[i], ]
  combinations = combn(unique(sub_total_df$group),2)
  for(j in seq(1,3)){
    res.ks.pw = apply(combinations, 2, ks_test_pairwise, sub_total_df, "precision", alt_methods[j])
    res.ks.pw = data.frame(res.ks.pw)
    names(res.ks.pw) = res.ks.pw[1,]
    res.ks.pw = t(res.ks.pw[-1,])
    write.csv(res.ks.pw, paste0(out_dir, "full_ks_test_result_normalized", "-", lib_size_repo[i], "-", alt_methods[j], ".csv"))
  }
}
```

## Using all targets df to do kld test
```{r}
lib_size_repo = unique(total_df$size)
union_df = data.frame()
for(i in seq(1, length(lib_size_repo))){
  sub_total_df = total_df[total_df$size==lib_size_repo[i], ]
  combinations = combn(unique(sub_total_df$group),2)
  res.ks.pw = apply(combinations, 2, kld_test_pairwise, sub_total_df, "precision")
  res.ks.pw = data.frame(res.ks.pw)
  names(res.ks.pw) = res.ks.pw[1,]
  res.ks.pw = data.frame(t(res.ks.pw[-1,]))
  res.ks.pw = tibble::add_column(res.ks.pw, comparison=rownames(res.ks.pw), .before = 1)
  colnames(res.ks.pw)[colnames(res.ks.pw)=="KLD"] <- paste0("lib_size_", lib_size_repo[i])
  if(i==1){
    union_df = res.ks.pw
  }
  else{
    union_df = dplyr::full_join(union_df, res.ks.pw, by="comparison")
  }
  # write.csv(res.ks.pw, paste0(out_dir, "full_kld_test_result_normalized", "-", lib_size_repo[i], ".csv"))
}
write.csv(union_df, paste0(out_dir, "full_kld_test_result_normalized", ".csv"), row.names = F)
```

# Perform pairwise wilcoxon test
```{r}
wilcox_test_pairwise = function(v, df, precision_var, alternative){
  x = df[df$group==v[1],precision_var]
  y = df[df$group==v[2],precision_var]
  res.wilcox = wilcox.test(x,y, alternative = alternative, paired = T)
  return(c("comparison"=paste0(v[1],"-", v[2]), res.wilcox$statistic, "p.value"=res.wilcox$p.value))
}
```

## Using original values
```{r}
lib_size_repo = unique(total_df_no_zero$size)
alt_methods = c("two.sided", "less", "greater")
for(i in seq(1, length(lib_size_repo))){
  sub_total_df = total_df[total_df_no_zero$size==lib_size_repo[i], ]
  combinations = combn(unique(sub_total_df$group),2)
  for(j in seq(1,3)){
    res.wilcox.pw = apply(combinations, 2, wilcox_test_pairwise, sub_total_df, "precision", alt_methods[j])
    res.wilcox.pw = data.frame(res.wilcox.pw)
    names(res.wilcox.pw) = res.wilcox.pw[1,]
    res.wilcox.pw = data.frame(t(res.wilcox.pw[-1,]))
    res.wilcox.pw$significancy = ifelse(res.wilcox.pw$p.value<0.05, "yes", "no")
    write.csv(res.wilcox.pw, paste0(out_dir, "full_wilcoxon_test_replace_0_by_0.01_result", "-", lib_size_repo[i], "-", alt_methods[j], ".csv"))
  }
}
```

# Apply non parametric pair-wise wilcox comparison
```{r}
res.wilcox.pw = pairwise.wilcox.test(total_df$precision, total_df$group, alternative="greater", p.adjust.method = "none")
res.wilcox.pw
```

# Verify results of cML1 vs A 
```{r}
cML1 = total_df[total_df$group=="cML1",]$precision
A = total_df[total_df$group=="A",]$precision
res.wilcox = wilcox.test(cML1, A, alternative = "greater")
res.wilcox$p.value == res.wilcox.pw$p.value["cML1", "A"]
```

# Extract comparison for cML1, cML5, C1, C5 vs A
```{r}
interested_p_values = c(res.wilcox.pw$p.value["cML1", "A"], res.wilcox.pw$p.value["cML5", "A"],
                        res.wilcox.pw$p.value["C1", "A"], res.wilcox.pw$p.value["C5", "A"])
interested_p_values < 0.05
```

All interested p-values are less than 0.05 indicating that for certain methods, they are outperformed than AutoDock.

## Using median df
```{r}
dfs = list(median_df, median_df_0.1_5, median_df_0.1_1)
names_df = c("0.1-100", "0.1-5", "0.1-1")
for(i in seq(1,3)){
  for(j in seq(1, 3)){
    combinations = combn(unique(dfs[[j]]$group),2)
    res.ks.pw = apply(combinations, 2, ks_test_pairwise, dfs[[j]], "median_prec", alt_methods[i])
    res.ks.pw = data.frame(res.ks.pw) 
    names(res.ks.pw) = res.ks.pw[1,]
    res.ks.pw = t(res.ks.pw[-1,])
    write.csv(res.ks.pw, paste0("median_ks_test_result", "-", alt_methods[i], "-", names_df[j], ".csv"))
  }
}
```

# Normalize histogram for precision
```{r}
x = runif(20, 0, 1)
y = rbeta(20, 20, 100)
hx = hist(x, breaks = seq(0,1,0.05), plot=F) # or hist(x,plot=FALSE) to avoid the plot of the histogram
hx$density = hx$counts/sum(hx$counts)
hy = hist(y, breaks = seq(0,1,0.05), plot=F) # or hist(x,plot=FALSE) to avoid the plot of the histogram
hy$density = hy$counts/sum(hy$counts)
plot(hx, freq = F)
plot(hy, freq = F)
library(LaplacesDemon)
a = KLD(hx$density, tx$density)
```


